Javelins with hyper3 objects

### 2025-11-28 inst/javelin.Rmd
soft link for hyper2.bib
thinko

---
title: "Javelins with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
abline(0,1)
ordertransplot(m1,m2)
```

>>>>

---
title: "Javelins with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
ordertransplot(m1,m2)
```
